\def \codeURL{https://github.com/celinesoeiro/TCM-Model}
\def \codeDOI{}
\def \dataURL{}
\def \dataDOI{}
\def \editorNAME{}
\def \editorORCID{}
\def \reviewerINAME{}
\def \reviewerIORCID{}
\def \reviewerIINAME{}
\def \reviewerIIORCID{}
\def \dateRECEIVED{}
\def \dateACCEPTED{}
\def \datePUBLISHED{}
\def \articleTITLE{[Re] Cortical network effects of subthalamic deep brain stimulation in a thalamo-cortical microcircuit model}
\def \articleTYPE{Replication}
\def \articleDOMAIN{Computational Neuroscience}
\def \articleBIBLIOGRAPHY{bibliography.bib}
\def \articleYEAR{2024}
\def \reviewURL{}
\def \articleABSTRACT{Parkinson's disease is a degenerative disorder of the central nervous system associated to motor and nonmotor symptoms. Local field potential recordings reveal an elevated power in the beta band ($\sim13-30$ Hz) as a key indicator of altered cortical activity in parkinsonism. Deep brain stimulation of the subthalamic nucleus has been successfully used in the treatment of Parkinson's disease by suppressing pathological activity in the beta band and alleviating motor symptoms. A possible mechanism to explain the efficacy of deep brain stimulation of the subthalamic nucleus is the antidromic activation of pyramidal neurons in the primary motor cortex. The firing of these neurons would have a modulatory effect on the activity of the thalamo-cortical loop, reducing power in the beta band. Recently, Farokhniaee and Lowery proposed a model of the thalamo-cortical microcircuit that simulates this mechanism. The Farokhniaee and Lowery model was implemented in Matlab, and the goal of this work is to reimplement it in Python and reproduce a selection of its results.}
\def \replicationCITE{Farokhniaee, AmirAli and Lowery, Madeleine M. (2021) Cortical network effects of subthalamic deep brain stimulation in a thalamo-cortical microcircuit model. J. Neural Eng. 18: 056006}
\def \replicationBIB{farokhniaee2021cortical}
\def \replicationURL{}
\def \replicationDOI{10.1088/1741-2552/abee50}
\def \contactNAME{Celine Soeiro}
\def \contactEMAIL{celinesoeiro@gmail.com}
\def \articleKEYWORDS{thalamo-cortical microcircuit, DBS, Parkinson's disease, Python}
\def \journalNAME{ReScience C}
\def \journalVOLUME{}
\def \journalISSUE{}
\def \articleNUMBER{}
\def \articleDOI{}
\def \authorsFULL{Celine Soeiro and Antonio Carlos Roque}
\def \authorsABBRV{C. Soeiro and A. C. Roque}
\def \authorsSHORT{Soeiro and Roque}
\title{\articleTITLE}
\date{}
\author[1,\orcid{0009-0008-9415-1219}]{Celine Soeiro}
\author[2,\orcid{0000-0003-1260-4840}]{Antonio C. Roque}
\affil[1]{Universidade de São Paulo, FFCLRP, Departamento de Computação e Matemática, Ribeirão Preto, Brazil}
\affil[2]{University of Sao Paulo, FFCLRP, Department of Physics, Ribeirao Preto, Brazil}
